# Quality {#quality .tabset .tabset-fade .tabset-pills}

## Overview {-}

A record is considered _completed_ when it has at least the sheets 
**anagrafica**, **accettazione**, **pim**, **dimissione** marked as completed.

---

## Complete records {.tabset .tabset-dropdown}

```{r, eval=!params$export}
qualityReportUI("q_overall")
```

```{r, context = "server", eval=!params$export}
qualityReport("q_overall", data = data_ranged[["full_filtered"]])
```

```{r, context = "server", eval=params$export, fig.height=11}
qualityReportStatic(data_ranged[["full_filtered"]](),
  params$q_overall_completed,
  params$q_overall_type
)
```








## Hospitalized {.tabset .tabset-dropdown}

```{r, context = "server"}
data_hosp <- reactive({
  dplyr::filter(data_ranged[["full_filtered"]](), !is.na(reparto))
})
```

Records are considered related to an "hospitalized" patient if the field 
**reparto** is not missing in the sheet **dimissione**.

```{r, eval=!params$export}
qualityReportUI("q_hosp")
```

```{r, context = "server", eval=!params$export}
qualityReport("q_hosp", data = data_hosp)
```

```{r, context = "server", eval=params$export, fig.height=11}
qualityReportStatic(data_hosp,
  params$q_hosp_completed,
  params$q_hosp_type
)
```








## Data errors {.tabset .tabset-dropdown}

Two types of errors are considered at the moment:

1. Missing data.

2. Outlier values out of reasonable range, i.e., which have a distance
   from the median that is farther than 1.5 times the inter quartile
   range.


### Missing values




```{r, eval=!params$export}
missReportUI("q_miss", data = full_records)
```

```{r, context = "server", eval=!params$export}
missReport("q_miss", data = data_ranged[["full_filtered"]])
```

```{r, context = "server", eval=params$export, fig.height=11}
missReportStatic(data = data_ranged[["full_filtered"]](),
                 center = params$q_miss_center)
```




### Possible errors into the data


For numerical variables, outliers are considered possible errors, i.e.
values farther than 1.5 times the inter quartile range from the median.

```{r, eval=!params$export}
outlierReportUI("q_err", data = full_records)
```

```{r, context = "server", eval=!params$export}
outlierReport("q_err", data = data_ranged[["outliers_filtered"]])
```

```{r, context = "server", eval=params$export, fig.height=11}
outlierReportStatic(data = data_ranged[["outliers_filtered"]](), center = params$q_err_center)
```


