# Descriptive and Demographic {#descriptives .tabset .tabset-fade .tabset-pills}

## Overview {-}

In Italy there are 23 medical surgical (M/S) Pediatric Intensive Care Units (PICUs):

- 11 in the north
- 8 in the center
- 4 in the south

of the country.

Data reported here analyze patients admitted in PICUs from
`r params$first_y` to `r params$last_y`.

Only children 0 -- 16 years old who have a severity score on admission
which allow to estimate a Standardized Mortality Ratio (SMR) were
considered.

Exclusion criteria were "preterm or > 16 years old", or not completed
data entry

---

<!-- ## PICUs {.tabset .tabset-dropdown} -->

<!-- ### Partecipating Units -->

<!-- foo -->

<!-- ### Number of beds -->

<!-- foo -->











## Demographics {.tabset .tabset-dropdown}

<!-- foo -->




### Gender

```{r, eval=!params$export}
descriptivesReportUI("d_gender", what = "gender")
```

```{r, context = "server", eval=!params$export}
descriptivesReport(
  "d_gender",
  data = data_ranged[["full_filtered"]],
  what = "gender"
)
```

```{r, context = "server", eval=params$export, fig.height=11}
descriptivesReportStatic(
  data_ranged[["full_filtered"]](),
  completed = params[["d_gender_completed"]],
  what = "gender"
)
```







### Ethnicity

```{r, eval=!params$export}
descriptivesReportUI("d_ethnicity", what = "etnia")
```

```{r, context = "server", eval=!params$export}
descriptivesReport(
  "d_ethnicity",
  data = data_ranged[["full_filtered"]],
  what = "etnia"
)
```

```{r, context = "server", eval=params$export, fig.height=11}
descriptivesReportStatic(
  data_ranged[["full_filtered"]](),
  completed = params[["d_ethnicity_completed"]],
  what = "etnia"
)
```






### Age

```{r, eval=!params$export}
descriptivesReportUI("d_ageclass", what = "age_class")
```

```{r, context = "server", eval=!params$export}
descriptivesReport(
  "d_ageclass",
  data = data_ranged[["full_filtered"]],
  what = "age_class"
)
```

```{r, context = "server", eval=params$export, fig.height=11}
descriptivesReportStatic(
  data_ranged[["full_filtered"]](),
  completed = params[["d_ageclass_completed"]],
  what = "age_class"
)
```
