# Descriptive and Demographic {#descriptives .tabset .tabset-fade .tabset-pills}

## Overview {-}

In Italy there are 23 medical surgical (M/S) Pediatric Intensive Care Units (PICUs):

- 11 in the north
- 8 in the center
- 4 in the south

of the country.

Data reported here analyze patients admitted in PICUs from
`r params$first_y` to `r params$last_y`.

Only children 0 -- 16 years old who have a severity score on admission
which allow to estimate a Standardized Mortality Ratio (SMR) were
considered.

Exclusion criteria were "preterm or > 16 years old", or not completed
data entry

---

## PICUs {.tabset .tabset-dropdown}

### Partecipating Units

foo

### Number of beds

foo











## Admissions {.tabset .tabset-dropdown}

foo




### Gender


```{r, eval=!params$export}
descriptivesReportUI_gender("d_gender")
```

```{r, context = "server", eval=!params$export}
descriptivesReport_gender("d_gender", data = data_ranged[["full_filtered"]])
```

```{r, context = "server", eval=params$export, fig.height=11}
descriptivesReportStatic_gender(data = data_ranged[["full_filtered"]], completed = params[["d_gender_completed"]])
```








### Ethnicity

```{r, eval=!params$export}
descriptivesReportUI_etnia("d_etnia")
```

```{r, context = "server", eval=!params$export}
descriptivesReport_etnia("d_etnia", data = data_ranged[["full_filtered"]])
```

```{r, context = "server", eval=params$export, fig.height=11}
descriptivesReportStatic_etnia(data = data_ranged[["full_filtered"]],
      completed = params[["d_etnia_completed"]])
```


### Age

```{r, eval=!params$export}
descriptivesReportUI_ageclass("d_ageclass")
```

```{r, context = "server", eval=!params$export}
descriptivesReport_ageclass("d_ageclass", data = data_ranged[["full_filtered"]])
```

```{r, context = "server", eval=params$export, fig.height=11}
descriptivesReportStatic_ageclass(data = data_ranged[["full_filtered"]],
      completed = params[["d_ageclass_completed"]])
```





















## Demographics {.tabset .tabset-dropdown}

foo
