# Type of Admission and Origin {#origin .tabset .tabset-fade .tabset-pills}

## Overview {-}

The system allow to distinguish the first from subsequent admissions in the same unit. Admission was coded as mode, type, origin

**Mode**:

- planned (defined as admission that might be postponed for 24 hours)
- unplanned

**Type**:

- medical
- surgical
- trauma

**Origin**:

- ward
- emergency room
- operating room
- other hospital
- home
- other origin


> number of admission for the same patient beside the first



## Planned and Unplunned {.tabset .tabset-dropdown}

### Overview

### Re-admissions

### Distribution by units

### Distribution by origin


## Origin and type {.tabset .tabset-dropdown}

### Overview

### Origin
```{r, eval=!params$export}
OriginReportUI_origin("d_origin")
```

```{r, context = "server", eval=!params$export}
OriginReport_origin("d_origin", data = data_ranged[["full_filtered"]])
```

```{r, context = "server", eval=params$export, fig.height=11}
OriginReportStatic_origin(data = data_ranged[["full_filtered"]],
      completed = params[["d_origin_completed"]])
```

### Other hospital
```{r, eval=!params$export}
OriginReportUI_altroosp("d_altroosp")
```

```{r, context = "server", eval=!params$export}
OriginReport_altroosp("d_altroosp", data = data_ranged[["full_filtered"]])
```

```{r, context = "server", eval=params$export, fig.height=11}
OriginReportStatic_altroosp(data = data_ranged[["full_filtered"]],
      completed = params[["d_altroosp_completed"]])
```
### Distribution by units

### Type
```{r, eval=!params$export}
OriginReportUI_tipologia("d_tipologia")
```

```{r, context = "server", eval=!params$export}
OriginReport_tipologia("d_tipologia", data = data_ranged[["full_filtered"]])
```

```{r, context = "server", eval=params$export, fig.height=11}
OriginReportStatic_tipologia(data = data_ranged[["full_filtered"]],
      completed = params[["d_tipologia_completed"]])
```

### Type of surgery
```{r, eval=!params$export}
OriginReportUI_tipochir("d_tipochir")
```

```{r, context = "server", eval=!params$export}
OriginReport_tipochir("d_tipochir", data = data_ranged[["full_filtered"]])
```

```{r, context = "server", eval=params$export, fig.height=11}
OriginReportStatic_tipochir(data = data_ranged[["full_filtered"]],
      completed = params[["d_tipochir_completed"]])
```

## Reasons {.tabset .tabset-dropdown}

### Post-operative PICUs admissions

### Medical PICUs admissions

### Trauma

### brain trauma

### PICUs admission after injuries
