# Type of Admission and Origin {#origin .tabset .tabset-fade .tabset-pills}

## Overview {-}

The system allow to distinguish the first from subsequent admissions in the same unit. Admission was coded as mode, type, origin, and reasons. All the metrics can be visualized stratified by gender and age class.

**Mode**:

- planned (defined as admission that might be postponed for 24 hours)
- unplanned
- re-admission


**Type**:

- medical
- surgical
- trauma

**Origin**:

- ward
- emergency room
- operating room
- other hospital
- home
- other origin


> number of admission for the same patient beside the first



## Mode  {.tabset .tabset-dropdown}

### Planned and Unplanned
```{r, eval=!params$export}
originReportUI("m_planned")
```

```{r, context = "server", eval=!params$export}
originReport(
  "m_planned",
  data = data_ranged[["full_filtered"]],
  what = "ricovero_progr"
)
```

```{r, context = "server", eval=params$export, fig.height=11}
originReportStatic(
  data = data_ranged[["full_filtered"]](),
  completed = params[["d_gender_completed"]],
  what = "ricovero_progr"
)
```

### Re-admissions

```{r, eval=!params$export}
originReportUI("m_admission")
```

```{r, context = "server", eval=!params$export}
originReport(
  "m_admission",
  data = data_ranged[["full_filtered"]],
  what = "redcap_repeat_instance"
)
```

```{r, context = "server", eval=params$export, fig.height=11}
originReportStatic(
  data = data_ranged[["full_filtered"]](),
  completed = params[["d_gender_completed"]],
  what = "redcap_repeat_instance"
)
```

## Origin and type {.tabset .tabset-dropdown}

### Overview

### Other hospital

### Type

### Type of surgery


## Reasons {.tabset .tabset-dropdown}

### Post-operative PICUs admissions

### Medical PICUs admissions

### Trauma

### brain trauma

### PICUs admission after injuries
