# Type of Admission and Origin {#origin .tabset .tabset-fade .tabset-pills}

## Overview {-}

The system allow to distinguish the first from subsequent admissions in the same unit. Admission was coded as mode, type, origin

**Mode**:

- planned (defined as admission that might be postponed for 24 hours)
- unplanned

**Type**:

- medical
- surgical
- trauma

**Origin**:

- ward
- emergency room
- operating room
- other hospital
- home
- other origin


> number of admission for the same patient beside the first



## Planned and Unplanned {.tabset .tabset-dropdown}

### Overview
```{r, eval=!params$export}
originReportUI("o_readmission")
```

```{r, context = "server", eval=!params$export}
originReport(
  "o_readmission",
  data = data_ranged[["full_filtered"]],
  what = "ricovero_progr"
)
```

```{r, context = "server", eval=params$export, fig.height=11}
originReportStatic(
  data = data_ranged[["full_filtered"]](),
  completed = params[["d_gender_completed"]],
  what = "ricovero_progr"
)
```

### Re-admissions

### Distribution by gender

### Distribution by age group


## Origin and type {.tabset .tabset-dropdown}

### Overview

### Other hospital

### Type

### Type of surgery


## Reasons {.tabset .tabset-dropdown}

### Post-operative PICUs admissions

### Medical PICUs admissions

### Trauma

### brain trauma

### PICUs admission after injuries
