# PICU Admissions {#ccc .tabset .tabset-fade .tabset-pills}

## Overview {-}

<!--Chronic complex condition definition was taken by the paper of Feudtner C et al: “Pediatric Deaths Attributable to
Complex Chronic Conditions: A Population-Based Study of Washington State, 1980-1997” published in Pediatrics in
2000 (106:205-209) and was defined as “any medical condition that can be reasonably expected to last at least 12
months, unless death intervenes, and to involve either one or more different organ systems”.
CCC were divided within 10 categories (defined macrodiagnosis): neurologic, neuromuscular, cardiologic,
oncoematologic, respiratory, syndromic, renal, metabolic, malformation, other.
Moreover, the system allows to record the specific chronic disease --> 



## Comorbidity on admission {.tabset .tabset-dropdown}

### Comorbidity on admission Yes/No
```{r, eval=!params$export}
admissionReportUI("m_mal_cronica")
```

```{r, context = "server", eval=!params$export}
admissionReport(
  "m_mal_cronica",
  data = data_ranged[["full_filtered"]],
  type = "centervar",
  what = "mal_cronica"
)
```

### Macro-diagnosis
```{r, eval=!params$export}
admissionReportUI("m_macro")
```

```{r, context = "server", eval=!params$export}
admissionReport(
  "m_macro",
  data = data_ranged[["full_filtered"]],
  type = "checkbox",
  dict = comorb  # internal db in data-raw/internal-data.R
)
```


<!--## CCC {.tabset .tabset-dropdown}  -->

<!--### Rate by center  -->

<!--### Type  -->

<!--### Age --> 

## POPC {.tabset .tabset-dropdown}
```{r, eval=!params$export}
admissionReportUI("m_popc")
```

```{r, context = "server", eval=!params$export}
admissionReport(
  "m_popc",
  data = data_ranged[["full_filtered"]],
  type = "centervar",
  what = "popc"
)
```
## Insufficienze d'organo  {.tabset .tabset-dropdown}

### Insufficienze d'organo Yes/No
```{r, eval=!params$export}
admissionReportUI("m_insuff_organo7")
```

```{r, context = "server", eval=!params$export}
admissionReport(
  "m_insuff_organo7",
  data = data_ranged[["full_filtered"]],
  type = "centervar",
  what = "insuff_organo7"
)
```

### Insufficienze d'organo macro
```{r, eval=!params$export}
admissionReportUI("m_insuff_organo")
```

```{r, context = "server", eval=!params$export}
admissionReport(
  "m_insuff_organo",
  data = data_ranged[["full_filtered"]],
  type = "checkbox",
  dict = insuff_organo  # internal db in data-raw/internal-data.R
)
```



## PIM2 and PIM3 {.tabset .tabset-dropdown}

The registry adopted, since the beginning, the Pediatric Index of Mortality (PIM) score. The PIM2 variables are
recorded and the risk of death is automatically calculated by the system. In 2013, after a revision of the coefficient of the variables, the new PIM3 score was published. We updated the PIM page with the new formula and since 2014 we calculate both the 2 and 3 version. Moreover, retrospectically, we collected all the new variables and through the new coefficients we derived the PIM3 score for all the patient in the registry.


### Severity
```{r, eval=!params$export}
admissionReportUI("adm_pim")
```

```{r, context = "server", eval=!params$export}
admissionReport(
  "adm_pim",
  data = data_ranged[["full_filtered"]],
  type = "centervar",
  what = "pim"
)
```

