# Length of stay (LOS) and Pediatric Intensive Care Unit (PICU) discharge {#los .tabset .tabset-fade .tabset-pills}

## Overview {-}



## LOS {.tabset .tabset-dropdown}

### Age

### Year

### Center

### Condition (CCC)

### Rate of los


## Discharge {.tabset .tabset-dropdown}

### Diagnosi di dimissione principale
```{r, eval=!params$export}
losReportUI("m_diagnosi")
```

```{r, context = "server", eval=!params$export}
losReport(
  "m_diagnosi",
  data = data_ranged[["full_filtered"]],
  what = "diagnosi"
)
```

```{r, context = "server", eval=params$export, fig.height=11}
losReportStatic(
  data = data_ranged[["full_filtered"]](),
  completed = params[["d_diagnosi_completed"]],
  what = "diagnosi"
)
```

### Diagnosi di dimissione secondaria
```{r, eval=!params$export}
losReportUI("m_diagnosi_2")
```

```{r, context = "server", eval=!params$export}
losReport(
  "m_diagnosi_2",
  data = data_ranged[["full_filtered"]],
  what = "diagnosi_2"
)
```

```{r, context = "server", eval=params$export, fig.height=11}
losReportStatic(
  data = data_ranged[["full_filtered"]](),
  completed = params[["d_diagnosi_2_completed"]],
  what = "diagnosi_2"
)
```

## POPC  {.tabset .tabset-dropdown}
```{r, eval=!params$export}
losReportUI("m_popc_dimissione")
```

```{r, context = "server", eval=!params$export}
losReport(
  "m_popc_dimissione",
  data = data_ranged[["full_filtered"]],
  what = "popc_dimissione"
)
```

```{r, context = "server", eval=params$export, fig.height=11}
losReportStatic(
  data = data_ranged[["full_filtered"]](),
  completed = params[["d_popc_dimissione_completed"]],
  what = "popc_dimissione"
)
```

## Accertamento di morte e donazione {.tabset .tabset-dropdown}

### Esito
```{r, eval=!params$export}
losReportUI("m_esito_tip")
```

```{r, context = "server", eval=!params$export}
losReport(
  "m_esito_tip",
  data = data_ranged[["full_filtered"]],
  what = "esito_tip"
)
```

```{r, context = "server", eval=params$export, fig.height=11}
losReportStatic(
  data = data_ranged[["full_filtered"]](),
  completed = params[["d_esito_tip_completed"]],
  what = "esito_tip"
)
```

### Decesso
```{r, eval=!params$export}
losReportUI("m_mod_decesso")
```

```{r, context = "server", eval=!params$export}
losReport(
  "m_mod_decesso",
  data = data_ranged[["full_filtered"]],
  what = "mod_decesso"
)
```

```{r, context = "server", eval=params$export, fig.height=11}
losReportStatic(
  data = data_ranged[["full_filtered"]](),
  completed = params[["d_mod_decesso_completed"]],
  what = "mod_decesso"
)
```


### Accertamento di morte
```{r, eval=!params$export}
losReportUI("m_deceduto")
```

```{r, context = "server", eval=!params$export}
losReport(
  "m_deceduto",
  data = data_ranged[["full_filtered"]],
  what = "deceduto"
)
```

```{r, context = "server", eval=params$export, fig.height=11}
losReportStatic(
  data = data_ranged[["full_filtered"]](),
  completed = params[["d_deceduto_completed"]],
  what = "deceduto"
)
```

### Prelievo di organi
```{r, eval=!params$export}
losReportUI("m_prelievo_organi")
```

```{r, context = "server", eval=!params$export}
losReport(
  "m_prelievo_organi",
  data = data_ranged[["full_filtered"]],
  what = "prelievo_organi"
)
```

```{r, context = "server", eval=params$export, fig.height=11}
losReportStatic(
  data = data_ranged[["full_filtered"]](),
  completed = params[["d_prelievo_organi_completed"]],
  what = "prelievo_organi"
)
```

### Destinazione
```{r, eval=!params$export}
losReportUI("m_destinazione")
```

```{r, context = "server", eval=!params$export}
losReport(
  "m_destinazione",
  data = data_ranged[["full_filtered"]],
  what = "destinazione"
)
```

```{r, context = "server", eval=params$export, fig.height=11}
losReportStatic(
  data = data_ranged[["full_filtered"]](),
  completed = params[["d_destinazione_completed"]],
  what = "destinazione"
)
```

## Standardized Mortality Ratio (SMR) {.tabset .tabset-dropdown}

The Standardized Mortality Ratio (SMR) was estimated as the ratio between observed deaths/expected deaths.
Expected deaths were derived as the sum of all the PIM scores for each category considered.

The new score seems to perform better than the old one, with a more adequate estimation of deaths and a more
correct SMR.

### Units


### PIM2 and PIM3

### Age

### Year

### Type


## Predictive mortality models {.tabset .tabset-dropdown}
