--- 
params:
  cache: FALSE
  export: FALSE

  q_overall_completed: "Completed"
  q_overall_type: "Proportion"
  q_hosp_completed: "Completed"
  q_hosp_type: "Proportion"
  q_miss_center: ""
  q_err_center: ""
  
  d_gender_completed: "Completed only"

title: "TIPNet inter-dynamical report"
author: "The Italian Pediatric Intensive Care Units Network (**TIPNet**) is part of the Italian Society of Pediatric and Neonatal Anesthesia and Intensive Care (**SARNePI**).
  </br>
  \\ \\ \\ \\ This report has been developed in collaboration with the Unit of Biostatistics, Epidemiology and Public Health (**UBEP**) --- University of Padova."

biblio-style: apalike
link-citations: yes
bibliography:
  - inst/bib/bibliography.bib
  - inst/bib/packages.bib

output:
  bookdown::html_document2:
    toc: true
    toc_float: true
    toc_depth: 2
    df_print: paged

runtime: shiny_prerendered
---


```{r setup, include=FALSE}
# This is run only once both to the render and server side, and it
# is the very first chunk of code that will be run

options(
  knitr.duplicate.label = 'allow',
  width = 144
)

knitr::opts_chunk$set(
  comment = "",
  cache = FALSE,
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  
  width      = 150,   # output size
  out.width = "100%", # part of output covered
  fig.width = 11,     # set size creation-time
  dpi = 192           # set output resolution (impact weight)
 )


all_attached <- paste0("package:", names(sessionInfo()$otherPkgs))
attempt::attempt(suppressWarnings(invisible(lapply(
  all_attached, detach, character.only = TRUE, unload = TRUE
))), silent = TRUE)




library(tidyverse)
library(lubridate)
library(plotly)
library(shiny)
library(glue) 
library(here)
library(DT)
library(fs)


if (getOption("tipnet.dev", FALSE)) {
    rstudioapi::documentSaveAll()
    roxygen2::roxygenise()
    devtools::load_all(quiet =  TRUE)
    cat("!!!!!!! dev !!!!!!!")
} else {
    devtools::load_all(quiet =  TRUE)
  # library(tipnet.report)
    cat("!!!!!!! prod !!!!!!")
}


last_file <- file.path(data_path(), "tipnet.rds")
is_to_update <- !fs::file_exists(last_file) ||
  (
    getOption("tipnet.auto_update", TRUE) &&
    is_expired(last_file, getOption("tipnet.max_days_update"))
  )

if (
  getOption("tipnet.force_update") ||
  is_to_update
) {
  db_update_from_server()
}

last_data_date <- as.Date(file.info(last_file)$mtime)


set.seed(1)
```


```{r data, include=FALSE, cache=params$cache, cache.extra=last_data_date}
# This run only once bot in the render and server side

# cache.extra option in the knitr tags here above needs to speed up
# normal computation and running time (render side) as the data are not
# changed. Note that server-side data are loaded from the render-side
# if included in the chunk named "data" (like this is), hence setting
# cache.extra provide a further speed up.

tipnet <- read_rds(last_file) 
tipnet_meta <- path(data_path(), "tipnet_meta.rds") %>% 
  read_rds()

iwalk(generate_main_data(), ~assign(.y, .x, pos = 1))
```


<!-- ```{r server-start, include = FALSE} -->
<!-- # this run only once on the server session when it starts (after -->
<!-- # setup and data chunks) -->
<!-- ``` -->

**Last report update**: `r as.Date(file.info('index.Rmd')$mtime)`  ---  **Last data update**: `r last_data_date`



# Colophon {-}

<style>
div.blue { background-color:#e6f0ff; border-radius: 5px; padding: 20px;}
</style>
<div class = "blue">

**Network coordinator**: Andrea Wolfler (Division of Anesthesia, Children’s Hospital G Gaslini – Genova) and Angela Amigoni (Pediatric Intensive Care Unit, University Hospital – Padova)

**In collaboration with**: Unit of Biostatistics, Epidemiology and Public Helath ([UBEP](https://www.unipd-ubep.it/)), [Department of Cardiac, Toracic, Vascular sciences and Public Health](https://www.dctv.unipd.it/) -- [University of Padova](https://www.unipd.it/) --- Interuniversity Consortium

- Dario Gregori (head of UBEP)
- Corrado Lanera, Giorgia Stoppa (Laboratory of Artificial Intelligence for Medical Sciences)
- Giulia Lorenzoni, Honoria Ocagli (Laboratory of Clinical Epidemiology)
- Rosanna Comoretto (Laboratory for Health Service Research)
- Matteo Martinato, Laura Nasato (Service for Clinical Trials and Biometrics)

**Steering Committee TIPNET (SCT)**: Angela Amigoni, Andrea Wolfler, Maria Cristina Mondardini, Dario Gregori, Matteo Martinato, Francesca Izzo, Marco Piastra, Paolo Biban, Rosanna Comoretto)

**IT Project Managers**: Dario Gregori, Corrado Lanera


**TIPNet study group** - participating center:

- Pediatric and Neonatal Intensive Care Unit, Children’s Hospital G Gaslini, Genova
- Division of Anesthesia and Intensive Care, Children’s Hospital Sant’Antonio e Biagio e Cesare Arrigo, Alessandria
- Department of Pediatrics, Ospedale Maggiore della Carità, Novara
- Division of Anesthesia and Intensive Care, Children’s Hospital V Buzzi, Milan
- Division of Pediatric Anesthesia and Intensive Care, Fondazione IRCCS Ca Granda, Ospedale Maggiore Policlinico, Milan
- Department of Neonatal and Paediatric Intensive Care, Azienda Ospedaliera Universitaria Integrata, Verona
- Department of Woman’s and Child’s Health, Pediatric ICU, University Hospital, Padova
- Division of Anesthesia and Intensive Care, Institute for Maternal and Child health, IRCCS Burlo Garofolo, Trieste
- Department of Pediatric Anesthesia and Intensive Care, Ospedale Sant’Orsola Malpighi, Bologna
- Division of Anesthesia and Intensive Care, Children’s Hospital Meyer, Firenze
- Department of Anesthesia and Intensive Care, Children’s Hospital Salesi, Ancona
- Division of Anesthesia and Intensive Care, Children’s Hospital Santobono-Pausillipon, Napoli
- Division of Anesthesia and Intensive Care, Children’s Hospital G Di Cristina, Palermo
- Division of Anesthesia and Intensive Care Ospedale Garibaldi – Nesima, Catania
- Department of Pediatrics Ospedale Policlinico –Universitario G Martino, Messina


</div>



```{r}
yearRangeUI("year_range", last_data_date)
```

```{r, context="server"}
data_ranged <- yearRange("year_range")
```






```{r, child = "005-quality.Rmd"}
```

```{r, child = "010-descriptives.Rmd"}
```

```{r, child = "020-origin.Rmd"}
```

```{r, child = "030-ccc.Rmd"}
```

```{r, child = "040-severity.Rmd"}
```

```{r, child = "045-inhospital.Rmd"}
```

```{r, child = "050-los.Rmd"}
```








```{r, results='asis', eval=!params$export}
cat("# Download current report {-}")
```

```{r, eval=!params$export}
actionButton("generate", "Generate Report", icon = icon("file"))
```

</br>

```{r, eval=!params$export}
shiny::downloadLink("report", "Download report", icon = icon("file"))
```

```{r, context="server", eval=!params$export}
report_path <- reactiveValues(filepath = NULL)

observeEvent(input$generate, {
      
  progress <- shiny::Progress$new()
  # Make sure it closes when we exit this reactive, even if there's an error
  on.exit(progress$close())

  progress$set(
    message = "Gathering data to build the report.",
    value = 0
  )

  static_dir <- "static"
  if (fs::dir_exists(static_dir)) fs::dir_delete(static_dir)
  dir <- normalizePath(fs::dir_create(static_dir))

  list.files(
    pattern = "\\.Rmd$|inst", 
    all.files = TRUE,
    include.dirs = TRUE
  ) %>% 
    stringr::str_subset("^index\\.Rmd$", negate = TRUE) %>% 
    file.copy(dir, recursive = TRUE, copy.date = TRUE)
  
  report_raw <- file.path(dir, "index.Rmd")
  report_out <- file.path(dir, "report.html")

  read_lines("index.Rmd") %>% 
    str_remove("^runtime: shiny_prerendered$") %>% 
    str_remove("\\.tabset \\.tabset-fade \\.tabset-pills") %>%
    write_lines(report_raw)

  # Set up parameters to pass to Rmd document
  params <- list(
    export = TRUE,

    q_overall_completed = input[[NS("q_overall", "completed")]],
    q_overall_type = input[[NS("q_overall", "type")]],
    q_hosp_completed = input[[NS("q_hosp", "completed")]],
    q_hosp_type = input[[NS("q_hosp", "type")]],
    q_miss_center = input[[NS("q_miss", "center")]],
    q_err_center = input[[NS("q_err", "center")]],
    
    d_gender_completed = input[[NS("d_gender", "completed")]]
  )

  progress$inc(amount = 0.4,
    message = "Building the report",
    detail = "This may take a while..."
  )
  
  withr::local_options(list(tipnet.dev = FALSE))
  rmarkdown::render(report_raw,
    output_file = report_out,
    params = params,
    envir = new.env(parent = globalenv())
  )  
  
  progress$set(value = 1,
    message = "Report build",
    detail = "Click the download link to download it.
      This window will disappear in 10 seconds."
  )
  Sys.sleep(10)

  report_path$filepath <- report_out
  

})

output$report <- downloadHandler(
  filename = paste0(today(), "_tipnet-report.html"),
  content  = function(file) file.copy(report_path$filepath, file)
)
```








# References {-}

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'inst/bib/packages.bib')
```
